LAGOS lake depth

### 2021-12-07 figures/02_depth_model.Rmd
format fig 4

gg_shape <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
    scale_fill_manual(values = hue_pal()(3)[1:2]) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      axis.text = element_text(size = 9.5),
      strip.text = element_blank(),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme(axis.text = element_blank(),
  axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

gg_shape <- cowplot::plot_grid(gg_shape[[1]],
  cowplot::plot_grid(
    cowplot::plot_grid(gg_shape[[1]], gg_shape[[2]],
      rel_widths = c(1, 0.85)),
    cowplot::plot_grid(gg_shape[[3]], gg_shape[[4]],
      rel_widths = c(1, 0.85)),
    ggdraw() + draw_label("Residual (m)", size = 10, y = 0.6),
    leg,
    nrow = 4, rel_heights = c(0.85, 1, 0.1, 0.15)),

@@

gg_reservoir <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = reservoir_class), alpha = 0.75, adjust = 1.3) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      strip.text = element_blank(),
      axis.text = element_text(size = 9.5),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_reservoir[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_reservoir[[2]] + labs(fill = "Reservoir class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_reservoir      <- lapply(gg_reservoir, rm_legend)
gg_reservoir[[2]] <- gg_reservoir[[2]] + theme(axis.text = element_blank(),
  axis.title = element_blank())
gg_reservoir[[3]] <- gg_reservoir[[3]] + theme(axis.title = element_blank())
gg_reservoir[[4]] <- gg_reservoir[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

gg_reservoir <- cowplot::plot_grid(gg_reservoir[[1]],
  cowplot::plot_grid(
    cowplot::plot_grid(gg_reservoir[[1]], gg_reservoir[[2]],
      rel_widths = c(1, 0.85)),
    cowplot::plot_grid(gg_reservoir[[3]], gg_reservoir[[4]],
      rel_widths = c(1, 0.85)),
    ggdraw() + draw_label("Residual (m)", size = 10, y = 0.6),
    leg,
    nrow = 4, rel_heights = c(0.85, 1, 0.1, 0.15)),
  ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  # draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  # draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  # draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) # +
# draw_label("Residual distribution",
#            x = 0.55, y = 0.99, size = 10, fontface = "bold")

cowplot::plot_grid(gg_shape, gg_reservoir, ncol = 2, rel_widths = c(1, 0.9))
```

>>>>

gg_shape <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
    scale_fill_manual(values = hue_pal()(3)[1:2]) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      axis.text = element_text(size = 9.5),
      strip.text = element_blank(),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme( # axis.text = element_blank(),
  axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

gg_shape <- cowplot::plot_grid(gg_shape[[1]],
  cowplot::plot_grid(
    cowplot::plot_grid(gg_shape[[1]], gg_shape[[2]],
      rel_widths = c(0.92, 1)),
    cowplot::plot_grid(gg_shape[[3]], gg_shape[[4]],
      rel_widths = c(1, 0.85)),
    ggdraw() + draw_label("Residual (m)", size = 10, y = 0.6),
    leg,
    nrow = 4, rel_heights = c(1, 1, 0.1, 0.15)),

@@

gg_reservoir <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = reservoir_class), alpha = 0.75, adjust = 1.3) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      strip.text = element_blank(),
      axis.text = element_text(size = 9.5),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_reservoir[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_reservoir[[2]] + labs(fill = "Reservoir class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_reservoir      <- lapply(gg_reservoir, rm_legend)
gg_reservoir[[2]] <- gg_reservoir[[2]] + theme( # axis.text = element_blank(),
  axis.title = element_blank())
gg_reservoir[[3]] <- gg_reservoir[[3]] + theme(axis.title = element_blank())
gg_reservoir[[4]] <- gg_reservoir[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

gg_reservoir <- cowplot::plot_grid(gg_reservoir[[1]],
  cowplot::plot_grid(
    cowplot::plot_grid(gg_reservoir[[1]], gg_reservoir[[2]],
      rel_widths = c(0.87, 1)),
    cowplot::plot_grid(gg_reservoir[[3]], gg_reservoir[[4]],
      rel_widths = c(1, 0.85)),
    ggdraw() + draw_label("Residual (m)", size = 10, y = 0.6),
    leg,
    nrow = 4, rel_heights = c(1, 1, 0.1, 0.15)),
  ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  # draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  # draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  # draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) # +
# draw_label("Residual distribution",
#            x = 0.55, y = 0.99, size = 10, fontface = "bold")

cowplot::plot_grid(gg_shape, gg_reservoir, ncol = 2, rel_widths = c(1, 0.9), labels = c("a", "b"))
```
